Visualizations for the manuscript

### 2022-03-09 metanalysis_visualization/manuscript_Figures.Rmd
code to generate a pannel with the ITS with seasonality by site

>>>>

## ITS with seasonality

### By site
```{r}
head(patient_count_psy_period_psy_all)
sites <- unique( patient_count_psy_period_psy_all$siteid )

p <- list()

for( i in 1:length(sites)){
  print(i)
  subset_site <- patient_count_psy_period_psy_all %>%
    filter( siteid == sites[i])
  ts_seasonal_percent_per_site <- lm(percentage ~ period*time + harmonic(month_year, 1, 12), subset_site)
  p[[i]] <- time_series_analysis_plotting(ts_seasonal_percent_per_site,
                              subset_site,
                              "percentage",
                              clearance_period = FALSE) +
  labs(title = sites[i],
       subtitle = "ITS with seasonality effect",
       x = "Calendar dates",
       y = "Percentage") +
     theme(strip.text = element_text(size = 10),
        axis.text.x = element_text(size = 8), 
        axis.text.y = element_text(size = 8), 
        axis.title.x = element_text(size = 8),
        axis.title.y = element_text(size = 8),
        title = element_text(size = 14),
        plot.subtitle = element_text(size = 12, face = "italic"))

}

g <- do.call(grid.arrange,p)
ggsave("its_seasonality_site.png",g, height = 20, width = 32, units = "cm")

### By country
```{r}
